---
title: "Machine Learning project about Human Activity Recognition"
output: html_document
---

## Executive summary
In this project we use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants, in order to predict the manner in which they do  the exercise.

## Preliminary Work
```{r, results='hide', warning=FALSE}
library(caret)
library(randomForest)
library(gbm)
library(plyr)
set.seed(123)
raw <- read.csv("pml-training.csv", na.strings=c("NA", "#DIV/0!", ""), stringsAsFactors = FALSE)
rawFinalTest <- read.csv("pml-testing.csv", na.strings=c("NA", "#DIV/0!", ""), stringsAsFactors = FALSE)
```
## Exploratory Data Analysis
```{r, results='hide'}
summary(raw)
str(raw)
```

2 things appear

* According name : Variables does not seem intersting : like X, timestamp variables, window variables
* It seems that variables contains a lot of NA

So we have to clean and prepare a training set and a test set

```{r}
raw$classe <- as.factor(raw$classe)
raw_NA <- as.data.frame(raw[,colSums(is.na(raw)) < 1000])
clean_data <- raw_NA[ , -c(1,3:7)]
inTrain <- createDataPartition(y=raw$classe, p=0.6, list=FALSE)
training <- clean_data[inTrain,]
testing <- clean_data[-inTrain,]
```

## Model
As we investigate factor variable, linear model is out of scope. So we can use the following models :

* Random Forest 
* Boosting

first let investigate correction between variables
```{r}
M <- abs(cor(training[,-c(1,54)]))
diag(M) <- 0
which(M > 0.8,arr.ind=T)
```

It appears that a preprocess seems necessary
Let's compare model

```{r, warning=FALSE}
modelFitRf <- train(training$classe ~ .,method="rf",preProcess="pca",data=training)
predictionRf <- predict(modelFitRf,testing)
confusionMatrix(testing$classe,predictionRf)
modelFitGbm <- train(training$classe ~ .,method="gbm",preProcess="pca",data=training, verbose=FALSE)
predictionGbm <- predict(modelFitGbm,testing)
confusionMatrix(testing$classe,predictionGbm)
```

Random Forest model seems appropriate

## Prediction

```{r}
prediction <- predict(modelFitRf,rawFinalTest)

pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
pml_write_files(prediction)
prediction
```